Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-05-21 TEBenchmarkPaper/article.tex
Minor changes

% Derived from the template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{csvsimple}
\usepackage{float}
\restylefloat{table}
\usepackage{hhline}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{arrows, calc, decorations.pathreplacing, positioning,
  shapes.geometric}
% etc.

@@

\begin{sloppypar}
  The precision and recall of three MTE tools are compared
  in~\cite{claessen2013automating}:
  IsaCoSy~\cite{Johansson.Dixon.Bundy:conjecture-generation},
  IsaScheme~\cite{Montano-Rivas.McCasland.Dixon.ea:2012} and
  HipSpec~\cite{Claessen_hipspec:automating}.\footnote{Unfortunately this
    comparison only reports prior results for each tool, rather than reproducing
    them. This makes the numbers less comparable, since each tool was tested
    with slightly different definitions (e.g. whether or not the exponential and
    maximum functions were included).} The definitions and ground truths for all
  three were taken from the standard library of the Isabelle proof assistant:
  since the library authors have gone to the effort of stating and proving these
  properties, and including them with every copy of their software, this is a good
  indication that they are interesting. Two sets of definitions were used: a
  theory of natural numbers; and a theory of lists (which we show in
  Figure~\ref{figure:list_theory} on page~\pageref{figure:list_theory}). With
  only two datapoints, each containing only a few definitions and properties (4
  functions and 12 properties, in the natural number example), it is difficult
  to draw general conclusions; yet despite these limitations we believe that
  this is a viable method to performing meaningful, objective analyses and
  comparisons for such tools. It is only with larger data sets that we can
  generalise the measured performance to different, especially \emph{novel},
  domains (which, after all, is the purpose of MTE tools). In addition, we might
  be concerned that such ``popular'' theories as the natural numbers may be
  unrepresentative of typical usage. For example, we would not expect the
  library functions in a typical verification problem to be as mathematically
  rich as number theory.
\end{sloppypar}

@@

Once such a problem set has been chosen, we must separate the theorem statements
from the definitions they reference. The latter will be used as input to the
MTE tools, whilst the former constitute the ground truth corpus of properties
against which to compare the output.

@@

\begin{itemize}
\item The result would be a single data point, which makes it difficult to
  infer performance \emph{in general}.
\item It is impractical to run existing MTE tools on ``large'' inputs,
  containing more than a few dozen definitions.
\end{itemize}

@@

Given a sample of definitions and a corresponding ground truth, the actual
execution of the MTE tool proceeds as in prior work. We must translate the
chosen definitions into the required input format, then we time the execution
with a timeout (e.g. 5 minutes). We use wall-clock time since this is most
relevant to a user's experience, it has a straightforward interpretation and
tracking it does not require intrusive alterations to a tool's implementation.
The downside is that comparisons must take hardware performance into account,
which would not be the case if time were measured by some proxy like number of
expressions evaluated.

>>>>

% Derived from the template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{csvsimple}
\usepackage[inline, shortlabels]{enumitem}
\usepackage{float}
\restylefloat{table}
\usepackage{hhline}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{arrows, calc, decorations.pathreplacing, positioning,
  shapes.geometric}
% etc.

@@

\begin{sloppypar}
  The precision and recall of three MTE tools are compared
  in~\cite{claessen2013automating}:
  IsaCoSy~\cite{Johansson.Dixon.Bundy:conjecture-generation},
  IsaScheme~\cite{Montano-Rivas.McCasland.Dixon.ea:2012} and
  HipSpec~\cite{Claessen_hipspec:automating}.\footnote{Unfortunately this
    comparison only reports prior results for each tool, rather than reproducing
    them. This makes the numbers less comparable, since each tool was tested
    with slightly different definitions (e.g. whether or not the exponential and
    maximum functions were included).} The definitions and ground truths for all
  three were taken from the standard library of the Isabelle proof assistant.
  The fact that the library authors expended the effort of stating, proving and
  bundling these properties with every copy of their software is a good
  indication that they are interesting. Two sets of definitions were used: a
  theory of natural numbers; and a theory of lists (which we show in
  Figure~\ref{figure:list_theory} on page~\pageref{figure:list_theory}). With
  only two datapoints, each containing only a few definitions and properties (4
  functions and 12 properties, in the natural number example), it is difficult
  to draw general conclusions; yet despite these limitations we believe that
  this is a viable method to performing meaningful, objective analyses and
  comparisons for such tools. It is only with larger data sets that we can
  generalise the measured performance to different, especially \emph{novel},
  domains (which, after all, is the purpose of MTE tools). In addition, we might
  be concerned that such ``popular'' theories as the natural numbers may be
  unrepresentative of typical usage. For example, we would not expect the
  library functions in a typical verification problem to be as mathematically
  rich as number theory.
\end{sloppypar}

@@

Once such a problem set has been chosen, we must separate the definitions from
the theorem statements which reference those definitions. The definitions will
be used as input to the MTE tools, whilst the theorem statements form the ground
truth corpus of properties (which tool output will be compared against).

@@

\begin{itemize}
\item The result would be a single data point, which makes it difficult to
  infer performance \emph{in general}.
\item It is impractical to run existing MTE tools on inputs containing more
  than a few dozen definitions.
\end{itemize}

@@

Given a sample of definitions and a corresponding ground truth, the actual
execution of the MTE tool proceeds as in prior work. We must translate the
chosen definitions into the required input format, then we time the execution
with a timeout (e.g. 5 minutes). We use wall-clock time since
\begin {enumerate*} [i) ]%
\item this is most relevant to a user's experience,
\item it has a straightforward interpretation and
\item measuring it does not require intrusive alterations to a tool's
  implementation.
\end {enumerate*}
The downside is that comparisons must take hardware performance into account,
which would not be the case if time were measured by some proxy like number of
expressions evaluated.
